Contextual Combinatorial Cascading Bandits

### 2016-01-31 contextual combinatorial cascading bandits.tex
update alpha, delta

To state our main theorem, we need some definitions. Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$. Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.

@@

We evaluate $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k, k\leq K$ have the form of $\gamma^{k-1}$ for some $\gamma$.

@@

In the first experiment, we compare $C^3$-UCB to CombCascade on synthetic problems. This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user. At first, we randomly choose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$. Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\| = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$. This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$. Next we generate the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.

@@

\begin{lemma} %lem:DeltaEstimate
	\label{lem:DeltaEstimate}
	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, 
	%and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, 
	then we have
	$$
		R(t, \bA_t) \leq B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
	By Lemma \ref{lem:estimateU}, $w_t \leq \bU_t$. Then
	\begin{align*}
		f(\bA_t, \bU_t) \geq \alpha f(\bA_t^{\bU_t}, \bU_t) \geq \alpha f(A_t^*, \bU_t) \geq \alpha f(A_t^*, w_t),
	\end{align*}
	where $f(\bA_t^{\bU_t}, \bU_t) = \max_{A \in \cS} f(A, \bU_t)$. The first inequality is because we choose $\bA_t$ by the $\alpha$-approximation oracle with input $\bU_t$; the second inequality is because the maximum of $f(\bA_t^{\bU_t}, \bU_t)$ given $\bU_t$; the third inequality is by the monotonicity of $f$ and the property $\bU_t \geq w_t$. Then
	\begin{align*}
		R(t, \bA_t) = &\alpha f(A_t^*, w_t) - f(\bA_t, w_t) \\
		\leq &f(\bA_t, \bU_t) - f(\bA_t, w_t).
	\end{align*}
	By Lipschitz continuity of $f$ and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
	$$
	f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
	$$
	Then we have
	\begin{align*}
		R(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
		\leq &B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
	\end{align*}
\end{proof}

Notice that the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following lemma.

\begin{lemma} %lem:DeltaEsimateWithP*
	\label{lem:DeltaEsimateWithP*}
	Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
	$$
	\EE_t[R(t, \bA_t)] \leq \frac{B}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
	$$
\end{lemma}
\begin{proof}
	\begin{align}
		&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
		=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
		=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
		\leq &\frac{B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
		\leq &\frac{B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
	\end{align}
	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$. Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
\end{proof}

@@

\begin{proof}[ of Theorem \ref{thm:main}]
	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
	\begin{align}
	&R(T) = \EE \left[\sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
	&\leq \EE \left[\frac{B}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
\end{proof}

@@

	Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
	\begin{align}
		&\EE_t[R(t, \bA_t)] \leq 2 \EE[R(t, \bB_t) \left. \right| \cH_t] \nonumber \\
		=& 2 \EE \left[ \left. R(t, \bB_t) \EE \left[ \left. \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
		=& 2\EE \left[ \left. R(t, \bB_t) \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
		\leq &\frac{8}{f_{t}^{\ast}} \EE \left[ \left. R(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
	\end{align}
	Next, we have
	\begin{equation} \label{eq:andstarbt}
		f(A_t^*, w_t) \leq f(A_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t),
	\end{equation}
	where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:andMonotonicity}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).

@@

\begin{proof}[of Theorem \ref{thm:and}]
	Similar to the proof of Theorem \ref{thm:main}, we have the following derivation:
	\begin{align}
	&R(n) = \EE \left[ \sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
	\leq& \EE \left[\sum_{t=1}^{n} \frac{8}{f^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sqrt{ \left(\sum_{t=1}^{n} \bO_t \right) \EE_t \left[\sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
	\leq& \EE \left[\frac{\sqrt{128}}{f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
	&\qquad \qquad \left. \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
	\leq& \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMCdetEst}
	\end{align}
\end{proof}

>>>>

To state our main theorem, we need some definitions. Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$. In the same spirit of \cite{kveton2015combinatorial}, let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.

@@

We evaluate $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.

@@

In the first experiment, we compare $C^3$-UCB to CombCascade on synthetic problems. This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user. At first, we randomly choose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$. Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$. This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$. Next we generate the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.

@@

\begin{lemma} %lem:DeltaEstimate
	\label{lem:DeltaEstimate}
	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, 
	%and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, 
	then we have
	$$
		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
	By Lemma \ref{lem:estimateU}, $w_t \leq \bU_t$. Then
	\begin{align*}
		f(\bA_t, \bU_t) \geq \alpha f(\bA_t^{\bU_t}, \bU_t) \geq \alpha f(A_t^*, \bU_t) \geq \alpha f(A_t^*, w_t),
	\end{align*}
	where $f(\bA_t^{\bU_t}, \bU_t) = \max_{A \in \cS} f(A, \bU_t)$. The first inequality is because we choose $\bA_t$ by the $\alpha$-approximation oracle with input $\bU_t$; the second inequality is because the maximum of $f(\bA_t^{\bU_t}, \bU_t)$ given $\bU_t$; the third inequality is by the monotonicity of $f$ and the property $\bU_t \geq w_t$. Then
	\begin{align*}
		R^{\alpha}(t, \bA_t) = &\alpha f(A_t^*, w_t) - f(\bA_t, w_t) \\
		\leq &f(\bA_t, \bU_t) - f(\bA_t, w_t).
	\end{align*}
	By Lipschitz continuity of $f$ and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
	$$
	f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
	$$
	Then we have
	\begin{align*}
		R^{\alpha}(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
		\leq &B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
	\end{align*}
\end{proof}

Notice that the upper bound of $R^{\alpha}(t, \bA_t)$ is in terms of all base arms of $\bA_t$. However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following lemma.

\begin{lemma} %lem:DeltaEsimateWithP*
	\label{lem:DeltaEsimateWithP*}
	Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
	$$
	\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq \frac{B}{p^*} \EE \left[ \left.\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
	$$
\end{lemma}
\begin{proof}
	\begin{align}
		&\EE[R^{\alpha}(t, \bA_t)|\cH_t]  \nonumber \\
		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
		\leq &\frac{B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
		\leq &\frac{B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
	\end{align}
	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$. Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
\end{proof}

@@

\begin{proof}[ of Theorem \ref{thm:main}]
	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
	\begin{align}
	&R^{\alpha}(n) = \EE \left[\sum_{t=1}^{n} \EE[R^{\alpha}(t, \bA_t) | \cH_t] \right] \notag\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE \left[ \left. \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right| \cH_t \right] \right] \label{eq:pfMdeltaEst}\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{n}(\delta) \EE \left[ \left. \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right] \right] \label{eq:pfMbeta}\\
	&\leq \EE \left[\frac{B}{p^*} \bbeta_n(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d / n} \right)} + \sqrt{\lambda} \right) \right. \notag\\
	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
\end{proof}

@@

	Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
	\begin{align}
		&\EE[R(t, \bA_t) | \cH_t] \leq 2 \EE[R(t, \bB_t) \left. \right| \cH_t] \nonumber \\
		=& 2 \EE \left[ \left. R(t, \bB_t) \EE \left[ \left. \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
		=& 2\EE \left[ \left. R(t, \bB_t) \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
		\leq &\frac{8}{f_{t}^{\ast}} \EE \left[ \left. R(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
	\end{align}
	Next, we have
	\begin{equation} \label{eq:andstarbt}
		f(A_t^*, w_t) \leq f(A_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t),
	\end{equation}
	where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:andMonotonicity}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).

@@

\begin{proof}[of Theorem \ref{thm:and}]
	Similar to the proof of Theorem \ref{thm:main}, we have the following derivation:
	\begin{align}
	&R(n) = \EE \left[ \sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
	\leq& \EE \left[\sum_{t=1}^{n} \frac{8}{f^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sqrt{ \left(\sum_{t=1}^{n} \bO_t \right) \EE_t \left[\sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
	\leq& \EE \left[\frac{\sqrt{128}}{f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d /n}\right) } + \sqrt{\lambda} \right) \right. \notag\\
	&\qquad \qquad \left. \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
	\leq& \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{ \ln [ (1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMCdetEst}
	\end{align}
\end{proof}
